From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-29 Pi+/paper/equivalence.tex
Text in equivalence

Finally, We show how to translate $\PiLang$ programs to $\PiHatLang$ programs.

\begin{definition}
  \begin{align*}
    \evalt_{0} & : U \to \Nat                                               \\
    \evalt_{1} & : (c : X \iso Y) \to \evalt_{0}(X) \iso \evalt_{0}(Y)      \\
    \evalt_{2} & : (\alpha : p \Iso q) \to \evalt_{1}(p) \Iso \evalt_{1}(q) \\
  \end{align*}
\end{definition}

To normalise a $\PiLang$ circuit, we translate it to $\PiHatLang$ and quote it to $\PiPlusLang$.

>>>>

Finally, we show how to translate $\PiLang$ programs to $\PiPlusLang$ programs. $\PiLang$ has two symmetric monoidal
structure, the additive and the multiplicative one. In $\PiPlusLang$, the additive structure can be used to build the
multiplicative structure, by defining multiplication as repeated addition.

\begin{definition}
  \begin{align*}
    O \times Y           & \defeq O                       \\
    I \times Y           & \defeq Y                       \\
    (X_1 + X_2) \times Y & \defeq X_1 \times Y + X_2 \times Y
  \end{align*}
\end{definition}

\begin{proposition}
  $\PiPlusCat$ has a symmetric monoidal structure with $I$ for the unit and $\times$ for the tensor product. With the
  two tensor products and the distributivity combinator, $\PiPlusCat$ has a rig structure.
\end{proposition}

Using this rig structure, we translate $\PiLang$ to $\PiPlusLang$.

\begin{definition}
  \begin{align*}
    \evalt_{0} & : U \to \UPlus                                             \\
    \evalt_{1} & : (c : X \iso Y) \to \evalt_{0}(X) \iso \evalt_{0}(Y)      \\
    \evalt_{2} & : (\alpha : p \Iso q) \to \evalt_{1}(p) \Iso \evalt_{1}(q) \\
  \end{align*}
\end{definition}

To normalise a $\PiLang$ circuit, we translate it to $\PiHatLang$, compute a permutation, and quote back it to
$\PiPlusLang$.
